---
title: "Compare Test and Prod"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: cosmo
---

Compare Test and Prod Rmd

```{r setup, echo=FALSE, warnings = FALSE}
```

``` {r}
# runtime: shiny # to make run faster? 

impactsummary <- sharetemptot_out %>%
  select(NIELSEN_SEGMENT,
           `Manufacturer`,
            `$`,
           `$ Previous`,
           `$ Diff`,
           `EQ`,
           `EQ Previous`,
           `EQ Diff`) %>%
  SumAll(.) %>%
  group_by(NIELSEN_SEGMENT) %>%
  mutate(`$ Share` = round((`$`/sum(`$`))*100, digits = 2),
         `EQ Share` = round((`EQ`/sum(`EQ`))*100, digits = 2),
         `$ Share Previous` = round((`$ Previous`/sum(`$ Previous`))*100, digits = 2),
         `EQ Share Previous` = round((`EQ Previous`/sum(`EQ Previous`))*100, digits = 2),
         `$ Share Diff` = `$ Share`-`$ Share Previous`,
         `EQ Share Diff` = `EQ Share`-`EQ Share Previous`,
         `$ % Change` = round((`$ Diff`/`$ Previous`)*100, digits = 2),
         `EQ % Change` = round((`EQ Diff`/`EQ Previous`)*100, digits = 2),
         `$ % Tot Change` = round((`$ Diff`/sum(`$ Previous`))*100, digits = 2),
         `EQ % Tot Change` = round((`EQ Diff`/sum(`EQ Previous`))*100, digits = 2)) %>%
  ungroup(.) %>%
  filter(`$ Share Diff` != 0 | `EQ Share Diff` != 0 | `$ % Change` != 0 | `EQ % Change` != 0) %>%
  select(
    NIELSEN_SEGMENT,
    `Manufacturer`,
    `$`,
    `$ Previous`,
    `$ Diff`,
    `$ % Change`,
    `$ % Tot Change`,
    `$ Share`,
    `$ Share Previous`,
    `$ Share Diff`,
    `EQ`,
    `EQ Previous`,
    `EQ Diff`,
    `EQ % Change`,
    `EQ % Tot Change`,
    `EQ Share`,
    `EQ Share Previous`,
    `EQ Share Diff`
  )


impactsummary2021 <- sharetemptot_out %>%
           filter(
             `Period Description` >= mdy(
               '01/09/2021') &
                 `Period Description` < mdy('01/08/2022')) %>%
  select(NIELSEN_SEGMENT,
           `Manufacturer`,
            `$`,
           `$ Previous`,
           `$ Diff`,
           `EQ`,
           `EQ Previous`,
           `EQ Diff`) %>%
  SumAll(.) %>%
  group_by(NIELSEN_SEGMENT) %>%
  mutate(`$ Share` = round((`$`/sum(`$`))*100, digits = 2),
         `EQ Share` = round((`EQ`/sum(`EQ`))*100, digits = 2),
         `$ Share Previous` = round((`$ Previous`/sum(`$ Previous`))*100, digits = 2),
         `EQ Share Previous` = round((`EQ Previous`/sum(`EQ Previous`))*100, digits = 2),
         `$ Share Diff` = `$ Share`-`$ Share Previous`,
         `EQ Share Diff` = `EQ Share`-`EQ Share Previous`,
         `$ % Change` = round((`$ Diff`/`$ Previous`)*100, digits = 2),
         `EQ % Change` = round((`EQ Diff`/`EQ Previous`)*100, digits = 2),
         `$ % Tot Change` = round((`$ Diff`/sum(`$ Previous`))*100, digits = 2),
         `EQ % Tot Change` = round((`EQ Diff`/sum(`EQ Previous`))*100, digits = 2)) %>%
  ungroup(.) %>%
  filter(`$ Share Diff` != 0 | `EQ Share Diff` != 0 | `$ % Change` != 0 | `EQ % Change` != 0) %>%
  select(
    NIELSEN_SEGMENT,
    `Manufacturer`,
    `$`,
    `$ Previous`,
    `$ Diff`,
    `$ % Change`,
    `$ % Tot Change`,
    `$ Share`,
    `$ Share Previous`,
    `$ Share Diff`,
    `EQ`,
    `EQ Previous`,
    `EQ Diff`,
    `EQ % Change`,
    `EQ % Tot Change`,
    `EQ Share`,
    `EQ Share Previous`,
    `EQ Share Diff`
  )

impactsummary2022 <- sharetemptot_out %>%
           filter(
             `Period Description` >= mdy('01/08/2022')) %>%
  select(NIELSEN_SEGMENT,
           `Manufacturer`,
            `$`,
           `$ Previous`,
           `$ Diff`,
           `EQ`,
           `EQ Previous`,
           `EQ Diff`) %>%
  SumAll(.) %>%
  group_by(NIELSEN_SEGMENT) %>%
  mutate(`$ Share` = round((`$`/sum(`$`))*100, digits = 2),
         `EQ Share` = round((`EQ`/sum(`EQ`))*100, digits = 2),
         `$ Share Previous` = round((`$ Previous`/sum(`$ Previous`))*100, digits = 2),
         `EQ Share Previous` = round((`EQ Previous`/sum(`EQ Previous`))*100, digits = 2),
         `$ Share Diff` = `$ Share`-`$ Share Previous`,
         `EQ Share Diff` = `EQ Share`-`EQ Share Previous`,
         `$ % Change` = round((`$ Diff`/`$ Previous`)*100, digits = 2),
         `EQ % Change` = round((`EQ Diff`/`EQ Previous`)*100, digits = 2),
         `$ % Tot Change` = round((`$ Diff`/sum(`$ Previous`))*100, digits = 2),
         `EQ % Tot Change` = round((`EQ Diff`/sum(`EQ Previous`))*100, digits = 2)) %>%
  ungroup(.)%>%
  filter(`$ Share Diff` != 0 | `EQ Share Diff` != 0 | `$ % Change` != 0 | `EQ % Change` != 0) %>%
  select(
    NIELSEN_SEGMENT,
    `Manufacturer`,
    `$`,
    `$ Previous`,
    `$ Diff`,
    `$ % Change`,
    `$ % Tot Change`,
    `$ Share`,
    `$ Share Previous`,
    `$ Share Diff`,
    `EQ`,
    `EQ Previous`,
    `EQ Diff`,
    `EQ % Change`,
    `EQ % Tot Change`,
    `EQ Share`,
    `EQ Share Previous`,
    `EQ Share Diff`
  )

outputdf <- NULL
thekeylist <- "UPC"
nameslist <- names(Test_Consumption_Char)
nameslist2 <- names(Consumption_Char)
nameslist <- intersect(nameslist, nameslist2)
Test_Consumption_Char1 <- Test_Consumption_Char %>% select(any_of(nameslist)) %>% distinct(.) #Changed here Test_Consumption_Char1 from Test_Consumption_Char
Test_Consumption_Char1 <- cleanNAs(Test_Consumption_Char1) #Changed here
Consumption_Char1 <- Consumption_Char %>% select(any_of(nameslist)) %>% cleanNAs(.) #Changed here
namesdiff <- nameslist[nameslist != thekeylist]
for (i in namesdiff)
{
  thekeylistcp <- thekeylist
  vars <- list.append(thekeylistcp, i)
  df_subseta <- Test_Consumption_Char1 %>% select(all_of(vars)) #Changed here
  df_subsetb <- Consumption_Char1 %>% select(all_of(vars)) #Changed here
  #converting to char avoid type conversion issues
  df_subseta[] <- as.data.frame(lapply(df_subseta, as.character))
  df_subsetb[] <- as.data.frame(lapply(df_subsetb, as.character))
  diffs1 <- anti_join(df_subseta, df_subsetb, by = vars)
  diffs2 <- anti_join(df_subsetb, df_subseta, by = vars)
  outputdftemp <- diffs1
  outputdftemp <- bind_rows(outputdftemp, diffs2)
  #key, field, new, old
  names(df_subseta) <- list.append(thekeylist, "new")
  names(df_subsetb) <- list.append(thekeylist, "old")
  outputdftemp <- outputdftemp %>% select(all_of(thekeylist)) %>% mutate(fieldchanged = i)
  outputdftemp <- left_join(outputdftemp, df_subseta, by = thekeylist)
  outputdftemp <- left_join(outputdftemp, df_subsetb, by = thekeylist)
  if(!is.null(outputdf)){
    outputdf <- bind_rows(outputdf, outputdftemp)
  }else{
    outputdf <- outputdftemp
  }
}
outputdf <- outputdf %>% distinct(.)
CharInfo <- Test_Consumption_Char %>% select(UPC, NIELSEN_SEGMENT, ITEM_DESC)

#remove where noted in added/dropped UPCs
outputdfitems <- outputdf %>% distinct(UPC)
outputdf <-
  outputdfitems %>% 
  anti_join(., newTestUPCs) %>% 
  anti_join(., droppedTestUPCs1) %>% 
  inner_join(., outputdf) %>% left_join(., CharInfo)

#EQ Changes
maxWE <- max(Consumption$`Period Description`)

prevEQ <- Test_Consumption %>% filter(`Period Description` < (maxWE - weeks(9))) %>% 
  select(-c("Period Description", "Market Description")) %>% 
  SumAll(.) %>% mutate(prev_EQ_Factor = round(EQ/Units, 2)) %>% select(UPC, prev_EQ_Factor, prev_EQ = EQ)
newEQ <- Test_Consumption %>% filter(`Period Description` <= maxWE &
                                       `Period Description` >= (maxWE - weeks(9))) %>% 
  select(-c("Period Description", "Market Description")) %>%
  SumAll(.) %>% mutate(new_EQ_Factor = round(EQ/Units, 2)) %>% select(UPC, new_EQ_Factor, new_EQ = EQ)

Char1 <- Test_Consumption_Char %>%
  distinct(UPC, NIELSEN_SEGMENT, `Manufacturer`, Subbrand)

outEQ <-
  inner_join(newEQ, prevEQ) %>%
  left_join(., Char1) %>% mutate(diffEQ = round(new_EQ_Factor - prev_EQ_Factor, 2),
                                       EQ = new_EQ + prev_EQ) %>%
  filter(diffEQ >= 0.5) %>%
  select (-c(prev_EQ, new_EQ)) 


#ARP Changes
maxWE <- max(Consumption$`Period Description`)

prevARP <- Test_Consumption %>% filter(`Period Description` < (maxWE - weeks(9))) %>% 
  select(-c("Period Description", "Market Description")) %>% 
  SumAll(.) %>% mutate(prev_ARP = round(`$`/Units, 2)) %>% select(UPC, prev_ARP, "prev_$" = `$`)
newARP <- Test_Consumption %>% filter(`Period Description` <= maxWE &
                                       `Period Description` >= (maxWE - weeks(9))) %>% 
  select(-c("Period Description", "Market Description")) %>%
  SumAll(.) %>% mutate(new_ARP = round(`$`/Units, 2)) %>% select(UPC, new_ARP, "new_$" = `$`)

Char1 <- Test_Consumption_Char %>%
  distinct(UPC, NIELSEN_SEGMENT, `Manufacturer`, Subbrand)

outARP <-
  inner_join(newARP, prevARP) %>%
  left_join(., Char1) %>% mutate(diffARP = round(new_ARP - prev_ARP, 2),
                                         `$` = `new_$` + `prev_$`) %>%
  filter(diffARP >= 0.01) %>%
  select (-c(`prev_$`, `new_$`)) 


# Key item char changes ####
Test_KeyChar <-
  Test_Consumption_Char %>% select(
    UPC,
    "TEST_ABT_BRAND" = ABT_BRAND,
    "TEST_ABT_SEGMENT" = ABT_SEGMENT,
    "TEST_ABT_SIZE RANGE" = `ABT_SIZE RANGE`,
    "TEST_TMC_ABBOTT_PRODUCT" = TMC_ABBOTT_PRODUCT,
    "TEST_TMC_FORMULA_SEGMENT" = TMC_FORMULA_SEGMENT,
    "TEST_TMC_INC_SHARE" = TMC_INC_SHARE,
    "TEST_TMC_MANUFACTURER" = TMC_MANUFACTURER,
    "TEST_TMC_SUBBRAND_CUSTOM" = TMC_SUBBRAND_CUSTOM,
    "TEST_NIELSEN_ABT_NAT_ORG" = NIELSEN_ABT_NAT_ORG
  )
    
KeyChar <-
  Consumption_Char %>% select(
    UPC,
    ABT_BRAND,
    ABT_SEGMENT,
    `ABT_SIZE RANGE`,
    TMC_ABBOTT_PRODUCT,
    TMC_FORMULA_SEGMENT,
    TMC_INC_SHARE,
    TMC_MANUFACTURER,
    TMC_SUBBRAND_CUSTOM,
    NIELSEN_ABT_NAT_ORG
  )

KeyItemDiff <- inner_join(Test_KeyChar, KeyChar) %>%
  mutate(
    "DIFF_ABT_BRAND" = if_else(`TEST_ABT_BRAND` == `ABT_BRAND`, FALSE, TRUE),
    "DIFF_ABT_SEGMENT" = if_else(`TEST_ABT_SEGMENT` == `ABT_SEGMENT`, FALSE, TRUE),
    "DIFF_ABT_SIZE RANGE" = if_else(`TEST_ABT_SIZE RANGE` == `ABT_SIZE RANGE`, FALSE, TRUE),
    "DIFF_TMC_ABBOTT_PRODUCT" = if_else(`TEST_TMC_ABBOTT_PRODUCT` == `TMC_ABBOTT_PRODUCT`, FALSE, TRUE),
    "DIFF_TMC_FORMULA_SEGMENT" = if_else(
      `TEST_TMC_FORMULA_SEGMENT` == `TMC_FORMULA_SEGMENT`,
      FALSE, TRUE
    ),
    "DIFF_TMC_INC_SHARE" = if_else(`TEST_TMC_INC_SHARE` == `TMC_INC_SHARE`, FALSE, TRUE),
    "DIFF_TMC_MANUFACTURER" = if_else(`TEST_TMC_MANUFACTURER` == `TMC_MANUFACTURER`, FALSE, TRUE),
    "DIFF_TMC_SUBBRAND_CUSTOM" = if_else(
      `TEST_TMC_SUBBRAND_CUSTOM` == `TMC_SUBBRAND_CUSTOM`,
      FALSE, TRUE
    ),
    "DIFF_NIELSEN_ABT_NAT_ORG" = if_else(`TEST_NIELSEN_ABT_NAT_ORG` == `NIELSEN_ABT_NAT_ORG`, FALSE, TRUE)
  )
KeyItemDiff <- KeyItemDiff %>% select(
  UPC,
  "TEST_ABT_BRAND",
  "ABT_BRAND",
  "DIFF_ABT_BRAND",
  "TEST_ABT_SEGMENT",
  "ABT_SEGMENT",
  "DIFF_ABT_SEGMENT",
  "TEST_ABT_SIZE RANGE",
  "ABT_SIZE RANGE",
  "DIFF_ABT_SIZE RANGE",
  "TEST_TMC_ABBOTT_PRODUCT",
  "TMC_ABBOTT_PRODUCT",
  "DIFF_TMC_ABBOTT_PRODUCT",
  "TEST_TMC_FORMULA_SEGMENT",
  "TMC_FORMULA_SEGMENT",
  "DIFF_TMC_FORMULA_SEGMENT",
  "TEST_TMC_INC_SHARE",
  "TMC_INC_SHARE",
  "DIFF_TMC_INC_SHARE",
  "TEST_TMC_MANUFACTURER",
  "TMC_MANUFACTURER",
  "DIFF_TMC_MANUFACTURER",
  "TEST_TMC_SUBBRAND_CUSTOM",
  "TMC_SUBBRAND_CUSTOM",
  "DIFF_TMC_SUBBRAND_CUSTOM",
  "TEST_NIELSEN_ABT_NAT_ORG",
  "NIELSEN_ABT_NAT_ORG",
  "DIFF_NIELSEN_ABT_NAT_ORG"
) %>% filter(
  `DIFF_ABT_BRAND` != FALSE |
    `DIFF_ABT_SEGMENT` != FALSE |
    `DIFF_ABT_SIZE RANGE` != FALSE |
    `DIFF_TMC_ABBOTT_PRODUCT` != FALSE |
    `DIFF_TMC_FORMULA_SEGMENT` != FALSE |
    `DIFF_TMC_INC_SHARE` != FALSE |
    `DIFF_TMC_MANUFACTURER` != FALSE |
    `DIFF_TMC_SUBBRAND_CUSTOM` != FALSE|
    `DIFF_NIELSEN_ABT_NAT_ORG` != FALSE
)
```

```{css my-content, echo = FALSE}
.rpivotTable{ overflow-x: scroll; }
```
Process Log
===================================== 

Column {data-width=600}
-------------------------------------
   
### ProcessLog

*** 

Process Log

```{r}
logfile1 <- includeMarkdown(paste0(RScriptdirectoryLoc,"TMC20log.Rmd"))
logfile1
```


Comparisons
=====================================   

*** 

Comparisons

Row {.tabset .tabset-fade}
-------------------------------------

### Retailer and Mfr Pivot

*** 

```{r}
if(nrow(compretandmfr)>0){
  rpivotTable(compretandmfr, rows = c("Period Description","Market Description"), 
            cols = c("NIELSEN_SEGMENT","Manufacturer"), aggregatorName = "Sum", vals = c("$ Diff", "EQ Diff"))
}
```


### Retailer and Mfr Pivot UPC

*** 

```{r}
if(nrow(sharetemptotUPC_out)>0) {
  rpivotTable(
    sharetemptotUPC_out,
    rows = c("Period Description", "Market Description", "UPC"),
    cols = c("NIELSEN_SEGMENT", "Manufacturer"),
    aggregatorName = "Sum",
    vals = c("$ Diff", "EQ Diff")
  )
}
```


### Full Impact Summary

*** 

All Time Impact

```{r}
impactsummary <- impactsummary %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(impactsummary, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))
```

### 2021 Impact Summary

*** 

2021 Impact

```{r}
impactsummary2021 <- impactsummary2021 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(impactsummary2021, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))
```

<!-- ### 2021 Impact Summary Pivot -->

<!-- ***  -->

<!-- ```{r} -->
<!-- if(nrow(impactsummary2021)>0) { -->
<!--   rpivotTable( -->
<!--     impactsummary2021, -->
<!--     rows = c("$ Share", "$ Share Previous", "EQ Share", "EQ Share Previous"), -->
<!--     cols = c("NIELSEN_SEGMENT", "Manufacturer"), -->
<!--     aggregatorName = "Sum", -->
<!--     vals = c("$ Share Diff", "EQ Diff") -->
<!--   ) -->
<!-- } -->
<!-- ``` -->

### 2022 Impact Summary

*** 

2022 Impact

```{r}
impactsummary2022 <- impactsummary2022 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(impactsummary2022, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))
```

<!-- ### 2022 Impact Summary Pivot -->

<!-- ***  -->

<!-- ```{r} -->
<!-- if(nrow(impactsummary2022)>0) { -->
<!--   rpivotTable( -->
<!--     impactsummary2022, -->
<!--     rows = c("$ Share", "$ Share Previous", "EQ Share", "EQ Share Previous"), -->
<!--     cols = c("NIELSEN_SEGMENT", "Manufacturer"), -->
<!--     aggregatorName = "Sum", -->
<!--     vals = c("$ Share Diff", "EQ Diff") -->
<!--   ) -->
<!-- } -->
<!-- ``` -->

### New ASIN UPC Combos

*** 

New ASIN UPC Combos

```{r}
newasinAssign <- newasinAssign %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(newasinAssign, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))

```

### New UPCs

*** 

New UPCs

```{r}
newTestUPCs <- newTestUPCs %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(newTestUPCs, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))

```

### Dropped ASIN UPC Combos

*** 

Dropped ASIN UPC Combos not being remapped.

```{r}
droppedasinAssign <- droppedasinAssign %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(droppedasinAssign, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))

```

### Dropped UPCs

*** 

Dropped UPCs not noted in AMZ

```{r}
droppedTestUPCs <- droppedTestUPCs %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(droppedTestUPCs, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollY = "425px"))

```

### Full Changed Items

*** 

Full Changed Items

```{r}
outputdf <- outputdf %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(outputdf, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollX = TRUE, scrollY = "425px",server =TRUE), filter = 'top')

```

### Key Changed Items

*** 

Key Changed Items

```{r}
KeyItemDiff <- KeyItemDiff %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(KeyItemDiff, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollX = TRUE,scrollY = "425px"), filter = 'top')

```


<!-- ### Key Changed Items Pivot -->

<!-- ***  -->

<!-- ```{r} -->
<!-- if(nrow(KeyItemDiff)>0) { -->
<!--   rpivotTable( -->
<!--     KeyItemDiff, -->
<!--     rows = c("UPC"), -->
<!--     cols = c( -->
<!--       "DIFF_ABT_BRAND", -->
<!--       "DIFF_ABT_SEGMENT", -->
<!--       "DIFF_ABT_SIZE_RANGE", -->
<!--       "DIFF_TMC_ABBOTT_PRODUCT", -->
<!--       "DIFF_ABT_SIZE RANGE", -->
<!--       "DIFF_TMC_ABBOTT_PRODUCT", -->
<!--       "DIFF_TMC_FORMULA_SEGMENT", -->
<!--       "DIFF_TMC_INC_SHARE", -->
<!--       "DIFF_TMC_MANUFACTURER", -->
<!--       "DIFF_TMC_SUBBRAND_CUSTOM", -->
<!--       "DIFF_NIELSEN_ABT_NAT_ORG" -->
<!--     ) -->
<!--   ) -->
<!-- } -->
<!-- ``` -->

### Inconsistent EQs

*** 

Items with inconsistent historical EQ factors

```{r}
outEQ <- outEQ %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(outEQ, options = list(columnDefs=list(list(targets="_all", class="dt-center")),scrollY = "425px"))
```

### Inconsistent ARP

*** 

Items with inconsistent historical ARP

```{r}
outARP <- outARP %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
datatable(outARP, options = list(columnDefs=list(list(targets="_all", class="dt-center")),scrollY = "425px"))
```

Costco $ Plot 
=====================================   

*** 

### Costco Sales by Segment/Week

-------------------------------------

```{r}
CostcoSegmentTTL <- read_csv(paste0(CSV_XLdirectoryLoc, "CostcoTotals.csv"))
CostcoSegmentTTL <- filter(CostcoSegmentTTL, `Period Description` >= maxWE - weeks(9))
fig <- CostcoSegmentTTL %>% 
  group_by(NIELSEN_SEGMENT) %>% 
  plot_ly(x= ~`Period Description`, y = ~`$`, type = 'scatter', color=~NIELSEN_SEGMENT, mode = 'lines') %>% layout(xaxis=list(title="Date"),yaxis=list(title="$"))
fig <- fig %>% layout(title = 'L9 Costco Sales by Segment')
fig

```

Comparison to Velocity
===================================== 
***

Row {.tabset .tabset-fade}
-------------------------------------

### VelocityComparison1

YoY comparison to Velocity data with Nielsen retailer data. High variance (1) is defined as a category-retailer combination with >50% difference in recent time periods vs YAG in Velocity vs the TMC output (from Connect data).

```{r}
VelCompSum <- read_csv(paste0(CSV_XLdirectoryLoc,"VelocityCompSummary.csv"))
names(VelCompSum) <- c("Market", "Brand", "TMC $ LW vs LY", "Velocity $ LW vs LY", "Variance $ LW vs LY", "TMC $ L13 vs LY", "Velocity $ L13 vs LY", "Variance $ L13 vs LY", "High Variance")
VelCompSum <- VelCompSum %>% mutate(`Variance $ LW vs LY` = round(`Variance $ LW vs LY` , 2),`Variance $ L13 vs LY` = round(`Variance $ L13 vs LY` , 2))
#VelCompSum <- VelCompSum %>% filter(`High Variance` == 1)
datatable(VelCompSum, filter = 'top', options = list(targets="_all", class="dt-center", pageLength = 50, scrollY = "400px",width = 'auto'))
```

### VelocityComparison2
*** 

Variance check of historical difference between Velocity and TMC based on L26.

```{r}
VelCompSum2 <- read_csv(paste0(CSV_XLdirectoryLoc,"VelocityCompSummary2.csv"))
names(VelCompSum2) <- c("Market", "Period", "Brand", "$ Vel", "$ TMC", "$ Variance", "flg_lw","Median", "3 sd", "Min Expected", "Max Expected", "High Variance")
#VelCompSum2 <- VelCompSum2 %>% filter(flg_lw == 1 & `High Variance` == 1)
datatable(VelCompSum2, filter = 'top', options = list(targets="_all", class="dt-center", pageLength = 50, scrollY = "400px",width = 'auto'))
```

Key Field Validations
=====================================   

*** 

Key Field Validations

Row {.tabset .tabset-fade}
-------------------------------------
  
### ItemsMissingKeyField

*** 

Items missing a key field. This could impact charts in TMC.

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "naChar.csv")), filter = 'top', options = list(pageLength = 50, scrollY = "500px", autoWidth = TRUE,columnDefs = list(list(width = '350px', targets = c(22,23,66)),list(width = 'auto', targets = "_all"))))
```

### ItemswithCalculatedFormulaSegment

*** 

Verify items that have a calculated formula segment.

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "naFormSegment.csv")), filter = 'top',options = list(pageLength = 50, scrollY = "500px", autoWidth = TRUE,columnDefs = list(list(width = '350px', targets = c(21,22,65)),list(width = '100', targets = c(1)),list(width = 'auto', targets = "_all"))))
```

### NewSubbrand

*** 

Verify items that have a subbrand not previously in the data.

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "NewSubbrands.csv")), filter = 'top', options = list(pageLength = 50, scrollY = "500px", autoWidth = TRUE,columnDefs = list(list(width = '350px', targets = c(21,22,65)),list(width = '100', targets = c(1)),list(width = 'auto', targets = "_all"))))
```

Items Missing An EQ
===================================== 
  
### ItemsMissingEQ

*** 

These items need an EQ added to the source data.

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "itemsMissingEQ.csv")), filter = 'top', options = list(pageLength = 50, scrollY = "500px", autoWidth = TRUE,columnDefs = list(list(width = '350px', targets = c(21,22,65)),list(width = 'auto', targets = "_all"))))
```

LW Outliers
=====================================   

*** 

Unusual LW volume items. These are flagged if they fall outside of 3 standard deviations of the L13 weeks.

### LWOutlier$

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "LWDolOutlierwide.csv")), options = list(pageLength = 50, scrollY = "425px"))
```

### LWOutlierEQ

```{r}
datatable(read_csv(paste0(CSV_XLdirectoryLoc, "LWEQOutlierwide.csv")), options = list(pageLength = 50, scrollY = "425px"))
```