---
title: "TMC Validation Report"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output:
  html_document:
    df_print: paged
    css: style.css
params:
  Segment: "INFANT FORMULA UA"
---

```{r setup, echo=FALSE, warnings=FALSE, include=FALSE}

impactsummary <- impactsummaryfun(sharetemptot_out)
impactsummary2021 <- impactsummaryfun(sharetemptot_out, '01/09/2021', '01/01/2022')
impactsummary2022 <- impactsummaryfun(sharetemptot_out, '01/08/2022',
                                      as.character(format(as.Date(maxWE),'%m/%d/%Y')))


# Key item char changes ####
Test_KeyChar <-
  Test_Consumption_Char %>% select(
    UPC,
    "TEST_ABT_BRAND" = ABT_BRAND,
    "TEST_ABT_SEGMENT" = ABT_SEGMENT,
    "TEST_ABT_SIZE RANGE" = `ABT_SIZE RANGE`,
    "TEST_TMC_ABBOTT_PRODUCT" = TMC_ABBOTT_PRODUCT,
    "TEST_TMC_FORMULA_SEGMENT" = TMC_FORMULA_SEGMENT,
    "TEST_TMC_INC_SHARE" = TMC_INC_SHARE,
    "TEST_TMC_MANUFACTURER" = TMC_MANUFACTURER,
    "TEST_TMC_SUBBRAND_CUSTOM" = TMC_SUBBRAND_CUSTOM,
    "TEST_NIELSEN_ABT_NAT_ORG" = NIELSEN_ABT_NAT_ORG
  )
KeyChar <-
  Consumption_Char %>% select(
    UPC,
    ABT_BRAND,
    ABT_SEGMENT,
    `ABT_SIZE RANGE`,
    TMC_ABBOTT_PRODUCT,
    TMC_FORMULA_SEGMENT,
    TMC_INC_SHARE,
    TMC_MANUFACTURER,
    TMC_SUBBRAND_CUSTOM,
    NIELSEN_ABT_NAT_ORG
  )

KeyItemDiff <- inner_join(Test_KeyChar, KeyChar) %>%
  mutate(
    "DIFF_ABT_BRAND" = if_else(`TEST_ABT_BRAND` == `ABT_BRAND`, TRUE, FALSE),
    "DIFF_ABT_SEGMENT" = if_else(`TEST_ABT_SEGMENT` == `ABT_SEGMENT`, TRUE, FALSE),
    "DIFF_ABT_SIZE RANGE" = if_else(`TEST_ABT_SIZE RANGE` == `ABT_SIZE RANGE`, TRUE, FALSE),
    "DIFF_TMC_ABBOTT_PRODUCT" = if_else(`TEST_TMC_ABBOTT_PRODUCT` == `TMC_ABBOTT_PRODUCT`, TRUE, FALSE),
    "DIFF_TMC_FORMULA_SEGMENT" = if_else(
      `TEST_TMC_FORMULA_SEGMENT` == `TMC_FORMULA_SEGMENT`,
      TRUE,
      FALSE
    ),
    "DIFF_TMC_INC_SHARE" = if_else(`TEST_TMC_INC_SHARE` == `TMC_INC_SHARE`, TRUE, FALSE),
    "DIFF_TMC_MANUFACTURER" = if_else(`TEST_TMC_MANUFACTURER` == `TMC_MANUFACTURER`, TRUE, FALSE),
    "DIFF_TMC_SUBBRAND_CUSTOM" = if_else(
      `TEST_TMC_SUBBRAND_CUSTOM` == `TMC_SUBBRAND_CUSTOM`,
      TRUE,
      FALSE
    ),
    "DIFF_NIELSEN_ABT_NAT_ORG" = if_else(`TEST_NIELSEN_ABT_NAT_ORG` == `NIELSEN_ABT_NAT_ORG`, TRUE, FALSE)
  )
KeyItemDiff <- KeyItemDiff %>% select(
  UPC,
  "TEST_ABT_BRAND",
  "ABT_BRAND",
  "DIFF_ABT_BRAND",
  "TEST_ABT_SEGMENT",
  "ABT_SEGMENT",
  "DIFF_ABT_SEGMENT",
  "TEST_ABT_SIZE RANGE",
  "ABT_SIZE RANGE",
  "DIFF_ABT_SIZE RANGE",
  "TEST_TMC_ABBOTT_PRODUCT",
  "TMC_ABBOTT_PRODUCT",
  "DIFF_TMC_ABBOTT_PRODUCT",
  "TEST_TMC_FORMULA_SEGMENT",
  "TMC_FORMULA_SEGMENT",
  "DIFF_TMC_FORMULA_SEGMENT",
  "TEST_TMC_INC_SHARE",
  "TMC_INC_SHARE",
  "DIFF_TMC_INC_SHARE",
  "TEST_TMC_MANUFACTURER",
  "TMC_MANUFACTURER",
  "DIFF_TMC_MANUFACTURER",
  "TEST_TMC_SUBBRAND_CUSTOM",
  "TMC_SUBBRAND_CUSTOM",
  "DIFF_TMC_SUBBRAND_CUSTOM",
  "TEST_NIELSEN_ABT_NAT_ORG",
  "NIELSEN_ABT_NAT_ORG",
  "DIFF_NIELSEN_ABT_NAT_ORG"
) %>% filter(
  `DIFF_ABT_BRAND` != TRUE |
    `DIFF_ABT_SEGMENT` != TRUE |
    `DIFF_ABT_SIZE RANGE` != TRUE |
    `DIFF_TMC_ABBOTT_PRODUCT` != TRUE |
    `DIFF_TMC_FORMULA_SEGMENT` != TRUE |
    `DIFF_TMC_INC_SHARE` != TRUE |
    `DIFF_TMC_MANUFACTURER` != TRUE |
    `DIFF_TMC_SUBBRAND_CUSTOM` != TRUE|
    `DIFF_NIELSEN_ABT_NAT_ORG` != TRUE
)

sharetemptotUPC_out1 <-
    sharetemptotUPC_out %>% filter(NIELSEN_SEGMENT == params$Segment) 

impactsummary2021 <- impactsummary2021 %>%
  filter(NIELSEN_SEGMENT == params$Segment) %>%
  mutate(
    `$ % Change` = sprintf("%1.2f%%", `$ % Change`),
    `$ % Tot Change` = sprintf("%1.2f%%", `$ % Tot Change`),
    `EQ % Change` = sprintf("%1.2f%%", `EQ % Change`),
    `EQ % Tot Change` = sprintf("%1.2f%%", `EQ % Tot Change`)
  ) %>% 
  select(
    Manufacturer,
    "$ MFR % Chg" = `$ % Change`,
    "$ Total % Chg" = `$ % Tot Change`,
    "$ Share Chg" = `$ Share Diff`,
    "EQ MFR % Chg" = `EQ % Change`,
    "EQ Total % Chg" = `EQ % Tot Change`,
    "EQ Share Chg" = `EQ Share Diff`
  )
impactsummary2022 <- impactsummary2022 %>%
  filter(NIELSEN_SEGMENT == params$Segment) %>%
  mutate(
    `$ % Change` = sprintf("%1.2f%%", `$ % Change`),
    `$ % Tot Change` = sprintf("%1.2f%%", `$ % Tot Change`),
    `EQ % Change` = sprintf("%1.2f%%", `EQ % Change`),
    `EQ % Tot Change` = sprintf("%1.2f%%", `EQ % Tot Change`)
  ) %>%
  select(
    Manufacturer,
    "$ MFR % Chg" = `$ % Change`,
    "$ Total % Chg" = `$ % Tot Change`,
    "$ Share Chg" = `$ Share Diff`,
    "EQ MFR % Chg" = `EQ % Change`,
    "EQ Total % Chg" = `EQ % Tot Change`,
    "EQ Share Chg" = `EQ Share Diff`
  )

KeyItemDiff1 <- KeyItemDiff %>% 
  filter(TEST_ABT_SEGMENT == params$Segment) %>% 
  mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))

newTestUPCs1 <- newTestUPCs %>% 
  filter(NIELSEN_SEGMENT == params$Segment) %>% 
  mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
```

## Restatement Summary for `r params$Segment`

`r if(nrow(impactsummary2021)>0){"### 2021 Restatement"}`

```{r restatement-summary1, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(impactsummary2021)>0) {
  knitr::kable(impactsummary2021,align=c(rep('c',times=ncol(impactsummary2021)))) %>%
  kable_classic(html_font = "Cambria")
}
```

`r if(nrow(impactsummary2022)>0){"### 2022 Restatement"}`

```{r restatement-summary2, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(impactsummary2022)>0) {
  knitr::kable(impactsummary2022,align=c(rep('c',times=ncol(impactsummary2022)))) %>%
  kable_classic(html_font = "Cambria")
}
```

`r if(nrow(sharetemptotUPC_out1)>0){"### Restatement Retailer Details"}`

```{r restatement-summary-1, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(sharetemptotUPC_out1)>0) {
  
  sharetemptotUPC_out2 <- sharetemptotUPC_out1 %>%
    left_join(., Calendar) %>%
    mutate(Year = as.character(Year)) %>%
    select(Year,
           Manufacturer,
           `Market Description`,
           `$`,
           `$ Diff`,
           `EQ`,
           `EQ Diff`) %>%
    group_by(Year, Manufacturer, `Market Description`) %>%
    SumAll(.) %>%
    filter(`$ Diff` != 0 | `EQ Diff` != 0) %>%
    mutate(`$` = scales::dollar(`$`),
           `$ Diff` = scales::dollar(`$ Diff`)) %>% 
    arrange(Year, `Market Description`, Manufacturer)

  if(nrow(sharetemptotUPC_out2)>0){
    sharetemptotUPC_out2 <-
    sharetemptotUPC_out2 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
  knitr::kable(sharetemptotUPC_out2,align=c(rep('c',times=ncol(sharetemptotUPC_out2)))) %>%
  kable_classic(html_font = "Cambria")
  }
}
```

`r if(nrow(sharetemptotUPC_out1)>0){"### Restatement Subbrand Details"}`

```{r restatement-summary-2, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(sharetemptotUPC_out1)>0) {
  
  sharetemptotUPC_out2 <- sharetemptotUPC_out1 %>%
    left_join(., Calendar) %>%
    mutate(Year = as.character(Year)) %>%
    select(Subbrand,
           `$`,
           `$ Diff`,
           `EQ`,
           `EQ Diff`) %>%
    group_by(Subbrand) %>%
    SumAll(.) %>%
    filter(`$ Diff` != 0 | `EQ Diff` != 0) %>%
    mutate(`$` = scales::dollar(`$`),
           `$ Diff` = scales::dollar(`$ Diff`)) %>% 
    arrange(Subbrand)

  if(nrow(sharetemptotUPC_out2)>0){
    sharetemptotUPC_out2 <-
    sharetemptotUPC_out2 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
  knitr::kable(sharetemptotUPC_out2,align=c(rep('c',times=ncol(sharetemptotUPC_out2)))) %>%
  kable_classic(html_font = "Cambria")
  }
}
```

`r if(nrow(sharetemptotUPC_out1)>0){"### Restatement UPC Details"}`

```{r restatement-summary-3, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(sharetemptotUPC_out1)>0) {
  
  sharetemptotUPC_out2 <- sharetemptotUPC_out1 %>%
    left_join(., Calendar) %>%
    mutate(Year = as.character(Year)) %>%
    select(Manufacturer,
           UPC,
           `$`,
           `$ Diff`,
           `EQ`,
           `EQ Diff`) %>%
    group_by(UPC, Manufacturer) %>%
    SumAll(.) %>%
    filter(`$ Diff` != 0 | `EQ Diff` != 0) %>%
    mutate(`$` = scales::dollar(`$`),
           `$ Diff` = scales::dollar(`$ Diff`)) %>% 
    arrange(Manufacturer, UPC) 
  if(nrow(sharetemptotUPC_out2)>0){
    sharetemptotUPC_out2 <-
    sharetemptotUPC_out2 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
  knitr::kable(sharetemptotUPC_out2,align=c(rep('c',times=ncol(sharetemptotUPC_out2)))) %>%
  kable_classic(html_font = "Cambria")
  }
}
```

`r if(nrow(sharetemptotUPC_out1)>0){"### Restatement Details"}`

```{r restatement-summary-4, echo=FALSE, warning=FALSE, message=FALSE}
if(nrow(sharetemptotUPC_out1)>0) {
  
  sharetemptotUPC_out2 <- sharetemptotUPC_out1 %>%
    left_join(., Calendar) %>%
    mutate(Year = as.character(Year)) %>%
    select(Year,
           `Market Description`,
           Manufacturer,
           Subbrand,
           UPC,
           `Market Description`,
           `$`,
           `$ Diff`,
           `EQ`,
           `EQ Diff`) %>%
    group_by(Year, `Market Description`, UPC, Manufacturer, Subbrand) %>%
    SumAll(.) %>%
    mutate(`$` = scales::dollar(`$`),
           `$ Diff` = scales::dollar(`$ Diff`)) %>% 
    arrange(Year, `Market Description`, Manufacturer, Subbrand, UPC)

  if(nrow(sharetemptotUPC_out2)>0){
    sharetemptotUPC_out2 <-
    sharetemptotUPC_out2 %>% mutate_if(is.numeric, ~ prettyNum(round(., 2), big.mark = ","))
  knitr::kable(sharetemptotUPC_out2,align=c(rep('c',times=ncol(sharetemptotUPC_out2)))) %>%
  kable_classic(html_font = "Cambria")
  }
}
```

`r if(nrow(KeyItemDiff1)>0){"### Key Changed Items"}`

```{r key-changed-items, echo=FALSE, warning=FALSE, message=FALSE}

if(nrow(KeyItemDiff1)>0){
  datatable(KeyItemDiff1, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollX = TRUE), filter = 'top')
}

```

`r if(nrow(newTestUPCs1)>0){"### New Items"}`

```{r new-items, echo=FALSE, warning=FALSE, message=FALSE}

if(nrow(newTestUPCs1)>0){
  datatable(newTestUPCs1, options = list(columnDefs=list(list(targets="_all", class="dt-center")), scrollX = TRUE), filter = 'top')
}

```
